WebApp zur Erfassung von Wildtiersichtungen

### 2024-12-17 bericht/AGI_report_kraftjul.tex
update AGI_report_kraftjul.tex to customize citation colors and add bibliography section

% Customize citation number color
\usepackage{xcolor} % Ensure xcolor is loaded
\DeclareFieldFormat{biblabel}{\textcolor{blue}{[#1]}} % Set citation color to blue
\renewcommand*{\mkbibbrackets}[1]{\textcolor{black}{[#1]}} % Ensure brackets are also black

@@

>>>>

% Customize citation number color
\usepackage{xcolor} % Load xcolor for color customization

% Change the color of citation numbers and brackets in text
\renewcommand*{\mkbibbrackets}[1]{\textcolor{blue}{[#1]}} % Brackets and numbers in blue

% Change the color of numbers in the bibliography
\DeclareFieldFormat{labelnumber}{\textcolor{blue}{#1}}

@@

\printbibliography
